Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-11 doc/report/msc-report.tex
little fixes and rewrites.

Analyzing data at a massive scale is one of the biggest challenges we face at
Last.fm. Interpreting patterns in user behaviour becomes a challenge when
millions of users interact in billions of combinations; the data sets must be
analyzed, summarized and presented visually in order to convey their meaning.

@@

Similar data stores exist; they generally use relational database systems as
their backing database. The novelty of our approach is to model multidimensional
data cubes on top of a column-oriented database, reaping the scalability
benefits of such databases.

@@

This chapters first section presents data warehouses and the concept of data
cubes. It then introduces common operations on data cubes: projections, slicing
and dicing, and aggregation.

@@

MapReduce is a framework for running jobs in parallel across multiple
machines. As the name implies, MapReduce is made up of two parts or
phases: map and reduce. The map phase consumes one piece of input at a
time (a piece of input can be a line from a log file, for example), and
emits an intermediate key and value. These keys and values are then
processed by the reduce phase, which emits the final key-value pairs.

@@

TODO: expand.

>>>>

Analyzing data at a massive scale is one of the biggest challenges that
Last.fm is facing. Interpreting patterns in user behaviour becomes a challenge
when millions of users interact in billions of combinations; the data sets
must be analyzed, summarized and presented visually.

@@

Similar data stores do exist but they generally use relational database systems
as their backing database. The novelty of our approach is to model
multidimensional data cubes on top of a distributed, column-oriented database to
reap the scalability benefits of such databases.

@@

This first section of this chapter presents data warehouses and the concept of
data cubes. It then introduces common operations on data cubes: projections,
slicing and dicing, and aggregation.

@@

MapReduce is a framework for distributed computations on large data sets in
parallel across multiple clustered computers. It was inspired by the map and
reduce functions commonly found in functional programming languages.

As the name implies, MapReduce is made up of two parts or phases: map and
reduce. The map phase consumes one piece of input at a time (a piece of input
can be a line from a log file, for example), and emits an intermediate key and
value. These keys and values are then processed by the reduce phase, which emits
the final key-value pairs.

@@

TODO: expand.
TODO: graph.
